The \dealii{} Library, Version 9.0

### 2018-04-19 9.0/paper.tex
minor updates, wrote a paragraph, update contributors

\section{Overview}

@@

\item
  Support for GPU

@@

\item
  Initial support for Gmsh

@@

\section{Significant changes to the library}

@@

\subsection{Feature 1}

\subsection{Feature 2}

\subsection{New and updated tutorial programs}
\marginpar{OLD}
In addition to the updated tutorial programs mentioned in the previous
section, this release of \dealii{} includes three new tutorials TODO: old:
\begin{itemize}
 \item {\bf step-55} explains how to solve the Stokes
 equations efficiently in parallel. It is a good introduction to solving
 systems of PDEs in parallel, discusses optimal block
 preconditioners, and demonstrates other aspects like error computation.
 Inverses of individual blocks of the linear system are approximated with an algebraic
 multigrid preconditioner.

@@

\subsection{New non-standard quadrature rules}

\begin{itemize}
\item QSimplex
\item QDuffy
\item QTrianglePolar
\item QSplit
\end{itemize}

Mostly used for BEM problems.

\subsection{Incompatible changes}

@@

\section{How to cite \dealii{}}\label{sec:cite}

@@

% \begin{minipage}{0.9\textwidth}%no page break in here please
% \begin{verbatim}
% @article{dealII82,
%   title = {The {\tt deal.{I}{I}} Library, Version 8.2},
%   author = {W. Bangerth and T. Heister and L. Heltai
%    and G. Kanschat and M. Kronbichler and M. Maier
%    and B. Turcksin and T. D. Young},
%   journal = {preprint},
%   year = {2015},
% }
% \end{verbatim} %  journal = {arXiv preprint \url{http://arxiv.org/abs/TODO}},
% \end{minipage}

@@

\marginpar{update}
\dealii{} can interface with many other libraries:
\begin{multicols}{2}
\begin{itemize}
\item Adol-c \cite{adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS, LAPACK
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item Threading Building Blocks \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people contributed code to
this release:\\
%
% get this from the changes/*/* files using the command listed in the
% release-tasks paper and remove the authors of this paper
%
\marginpar{update}
  Rajat Arora,
  Mauro Bardelloni,
  Conrad Clevenger,
  Sam Cox,
  Toby D. Young,
  Juliane Dannberg,
  Nicola Demo,
  Patrick Esser,
  Niklas Fehn,
  Joscha Gedicke,
  Nicola Giuliani,
  Sebastian Gonzalez-Pintor,
  Ryan Grove,
  Michael Harmon,
  Daniel Jodlbauer,
  Guido Kanschat,
  Justin Kauffman,
  Eldar Khattatov ,
  Uwe Koecher,
  Alex Kokomov,
  Paul Kuberry,
  Dustin Kumor,
  Konstantin Ladutenko,
  Karl Ljungkvist,
  Andrew McBride,
  Mathias Mentler,
  Andrea Mola,
  Dragan Nikolic,
  Vaibhav Palkar,
  Spencer Patty,
  Jonathan Perry-Houts,
  Giuseppe Pitton,
  Ce Qin,
  Jonathan Robey,
  Mayank Sabharwal,
  Ali Samii,
  Alberto Sartori,
  Daniel Shapero,
  Martin Steigemann,
  Jihuan Tian,
  Jaeryun Yim,
  Liang Zhao

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}

@@

\item
  Support for GPU
  \marginpar{paragraph for CUDA missing}

@@

\item
  Initial support for Gmsh.
  \emph{[--- Do we actually provide any functionality with the GMSH
  executable yet? ---]}
  \marginpar{TODO}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Significant changes to the library}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Feature 1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Feature 2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{New and updated tutorial programs}

\marginpar{OLD}
In addition to the updated tutorial programs mentioned in the previous
section, this release of \dealii{} includes three new tutorials TODO: old:
\begin{itemize}
 \item {\bf step-55} explains how to solve the Stokes
 equations efficiently in parallel. It is a good introduction to solving
 systems of PDEs in parallel, discusses optimal block
 preconditioners, and demonstrates other aspects like error computation.
 Inverses of individual blocks of the linear system are approximated with an algebraic
 multigrid preconditioner.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{New non-standard quadrature rules}

A number of non-standard, special-purpose quadrature rules have been
implemented. Among those are quadrature formulas that support
\begin{itemize}
  \item
    truncating standard formulas to simplical domains (\texttt{Qsimplex}),
  \item
    singular transformations of the unit cell to the unit simplex
    (\texttt{QDuffy}),
  \item
    composition of simplical quadrature rules to a combined rule on the
    unit cell (\texttt{QSplit}),
  \item
    transformation of the unit square to polar coordinates
    (\texttt{QTrianglePolar}).
\end{itemize}
These new quadrature rule greatly help to integrate singular domains. They
are mainly used in Boundary Element Methods.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Incompatible changes}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How to cite \dealii{}}\label{sec:cite}

@@

@@

\marginpar{update}
\dealii{} can interface with many other libraries:
\begin{multicols}{3}
\begin{itemize}
\item Adol-c \cite{adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS, LAPACK
\item GSL \cite{gsl2016}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
\item NetCDF \cite{rew1990netcdf}
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people contributed code to
this release:\\
%
% get this from the changes/*/* files using the command listed in the
% release-tasks paper and remove the authors of this paper
%
% Updated 2018-04-19
Julian Andrej,
Rajat Arora,
Lucas Campos,
Praveen Chandrashekar,
Jie Cheng,
Emma Cinatl,
Conrad Clevenger,
Ester Comellas,
Sambit Das,
Giovanni Di Ilio,
Nivesh Dommaraju,
Marc Fehling,
Niklas Fehn,
Menno Fraters,
Anian Fuchs,
Daniel Garcia-Sanchez,
Nicola Giuliani,
Anne Glerum,
Christoph Goering,
Alexander Grayver,
Samuel Imfeld,
Daniel Jodlbauer,
Guido Kanschat,
Vishal Kenchan,
Andreas Kergassner,
Eldar Khattatov,
Ingo Kligge,
Uwe Köcher,
Joachim Kopp,
Ross Kynch,
Konstantin Ladutenko,
Tulio Ligneul,
Karl Ljungkvist,
Santiago Ospina,
Alexey Ozeritsky,
Dirk Peschka,
Simon Puchert,
E. G. Puckett,
Lei Qiao,
Ce Qin,
Jonathan Robey,
Alberto Sartori,
Daniel Shapero,
Ben Shields,
Simon Sticko,
Oliver Sutton,
Zhuoran Wang,
Xiaoyu Wei,
Michał Wichrowski,
Julius Witte,
Feimi Yu,
Weixiong Zheng.
